---
title: "Let me tell you"
author: "Xinghao"
date: "January 19, 2018"
output: html_document
---
### Evaluation and Expression

"substitute" and "quote" works similarly, they return same data type withou any 
replcament in "substitute" function. 

In "eval", we can set the enviroment or list or data frame, on which we can apply 
conditions in "quote" or "substitute".

```{r}
x <- 15
new_env <- new.env()
new_env$x <- 25

eval(quote(x))
eval(quote(x), envir = new_env)
eval(quote(x), envir = parent.frame())

mtcars[eval(quote(mpg > x), mtcars, new_env), ]
mtcars[eval(quote(mpg > x), mtcars, parent.frame()), ]
```

Difference between "quote" and "substitute"

```{r}
check_difference <- function(x) {
  list(quote(x), substitute(x), x)
}

test_value <- 100
check_difference(test_value)
```

So, based on their difference, substitute is more popular in most of the 
functions.

<br><br/>
<br><br/>

```{r}
# -- Condition when the expression is not quoted at a proper time
subset2 <- function(x, condition) {
  condition_call <- substitute(condition)
  r <- eval(condition_call, x, parent.frame())
  x[r, ]
}

scramble <- function(x) x[sample(nrow(x)), ]

subscramble <- function(x, condition) {
  scramble(subset2(x, condition))
}
```

conditon is not quoted until subset2 function, which makes the condition not 
transmitted to subset2 successfully.

```{r, error = T}
subscramble(mtcars, mpg >= 4)

```

To fix this, when function calls functions, make sure conditions are quoted in 
advance before it goes into a function.

<br><br/>
<br><br/>

Now let's look at the expression

"Call" is just like a list, it contains all the arguments in function you want
to call and you can change the call based on its list-like structure.

```{r}
test_call <- quote(read.csv("test.csv", row.names = F))
# list-like structure
test_call$row.names
test_call[[3]]
test_call$col.names <- T
test_call
test_call$col.names <- NULL
test_call

# make function call more standard
pryr::standardise_call(test_call)

# generate call
new_call <- as.call(list(quote(mean), quote(c(1:25, NA)), "na.rm" = quote(T)))
eval(new_call)
```

Next, we need some complicated manipulations on calls.

```{r}
# update a call on a "formula level"
get_new_formula <- function(object, formula, ...) {
  new_args <- pryr::dots(...)
  # update call on formula
  object$call$formula <- update.formula(formula(object), formula)
  # update call on args
  object$call <- pryr::modify_call(object$call, new_args)
  eval(object$call)
}

old_reg <- lm(mpg~vs, data = mtcars)
# before update
old_reg
# after update
get_new_formula(old_reg, formula = .~. + cyl, weights = wt)

```


### Environment

Environment is pretty straightforwad, here we just talk about some trichy parts
of environments in r.

```{r}
test_env <- new.env()
# hide your variable in that environment
test_env$a <- 1
test_env$.a <- 2
# list all variable names
ls(test_env)
ls(test_env, all.names = T)
# list structures of all variables
ls.str(test_env)
ls.str(test_env, all.names = T)
```

Set NULL to variable will not delete the variable in that environment, better
method is to use rm().

<br><br/>

Function environments

```{r}
# -- enclosing environments
# where the function is created, it determines how the function finds value
environment(mean)

# -- binding environments
# where the function is stored, it determines how we find the function
pryr::where("mean")

# -- execution environments
# environment created to host execution, its parent is envlosing environment
plus <- function(x) {
  function(y) x + y
}
plus_one <- plus(1)
environment(plus_one) # every time is different
identical(parent.env(environment(plus_one)), environment(plus))

# -- calling environments
# the environments where the function is called, use parent.frame() to get
# execution environment has two parents: enclosing and calling, usually it only
# uses enclosing, use parent.frame() to access calling environment
f2 <- function() {
  x <- 10
  function() {
    def <- get("x", environment())
    cll <- get("x", parent.frame())
    list(defined = def, called = cll,
         "enclosing environment" = environment(),
         "calling environment" = parent.frame())
  }
}
g2 <- f2()
x <- 20
str(g2())

```


```{r}
# An example of tricky environment
fun1 <- function() x

fun2 <- function() {
  x <- 1
  fun1()
}

fun3 <- function() {
  x <- 1
  environment(fun1) <- environment()
  fun1()
}

x <- 3
# -- original environment
fun2()
# -- changed environment
fun3()

```

Namespaces

When overwrite some functions in global environment, it doesn't affect some
package functions because those package functions use package namespace (known 
as ::) to get those internal functions in package rather than the functions in 
global environment. 

Also, when try to export some functions from package (which means those 
functions are available outside the package), use :: avoids conflicting with
functions from other packages.

Loading makes the package available in memory but not in the search path. Still 
need :: to access functions in that package. loadNamespace() throws error and
requireNamespace() returns FALSE.

Attaching makes the package in search path. library() throws error and require()
returns FALSE.

<br><br/>
<br><br/>

Parsing and deparsing

parse() and deparse() are used to do the conversion between string and expression

```{r}
# -- "run code" to expression 
test_expr <- quote(y <- 1 + 2)
# -- expression to text (string)
test_text <- deparse(test_expr)
# -- text (string) to expression
test_expr2 <- parse(text = test_text)
# -- expression to "run code"
eval(test_expr2)

y
```





